\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/eval.tex
table one column
removed reference to and , mult gates

\subsubsection*{Linear classifier}The results for linear
classification are in Table~\ref{tab:lc}. The
input and the model are both vectors of length $d$. The columns
``Prev. time'' and ``Prev. comm'' show the time and the total
network communication reported by Bost et al.~\cite{shafindss} for a
network setting with 40ms
round trip time, which is same as our WAN setting. The total execution
time
of \tool generated code in the LAN and the WAN setting is reported
next, followed by the total communication.
We observe that the \tool code performance matches the hand-crafted protocol of Bost
et al., and the programmer effort in \tool is just 20
lines (last column in the table) of high-level code in the \tool
source language. %\aseem{They write circuits,
 % right?} \nc{Actually, they have a specific protocols for dot product and comparison and also say that their developer effort is minimal as they have to write two function calls to these protocols :).} 
 Our execution time is dominated by the multiplications and
boolean-ands.
The number of boolean-and gates (\#And) remains constant for both the
benchmarks as they reflect the number of gates required for a
single  comparison, while the number of
multiplication gates (\#Mul) is the same as the model size $d$.
%% The
%% last column shows the lines of code of \tool program, which is also
%% independent of the model size.

@@

\subsubsection*{Decision trees}
Our decision tree numbers in Table~\ref{tab:dt} further validate
this claim. We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
describe specialized protocols for trees and forests (that perform
better than~\cite{shafindss}).
Similar to Bost et al.~\cite{shafindss}, they also remarks that these
computations are infeasible with Yao-based 2PC.
Again, we observe that
the performance of \tool generated generic 2PC
code is competitive with specialized protocols. 
\setlength\tabcolsep{8pt}
\begin{table*}
\begin{tabular}{c|c|c|c|c |c|c|c|c|c|c}
Dataset & $d$  & Prev. time (s) & Prev. Comm (kb) & LAN (s) & WAN (s) & Comm. (kb)  & \#And & \#Mul & \#Gates & LOC\\
\hline
Breast cancer & 30 & 0.3 & 36 & 0.1 & 0.3 & 25 & 95 & 30 & 727 & 20\\
\hline
Credit & 47 & 0.3 & 41 & 0.1 & 0.3 & 36 & 95 & 47 & 795 & 20\\
\hline
\end{tabular}

 \caption{Linear classification results. We compare our results (columns 5, 6, 7) with~\cite{shafindss} (columns 3 and 4)}
 \label{tab:lc} 
\end{table*}
\setlength\tabcolsep{7pt}
\begin{table*}
\begin{tabular}{c|c|c|c|c|c |c|c|c|c|c|c}
Dataset & $d$ & $F$ & Prev. time (s) & Prev. Comm (Mb) & LAN (s) & WAN (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates  & LOC\\
\hline
Nursery & 5 & 9 & 1.5 & 0.2 & 0.1 & 0.4 & 0.6 & 13k & 0 & 73k & 50\\
\hline
Audiology & 24 & 70 & 3.9 & 2.0 & 1.5 & 2.9 & 37 & 750k & 0 & 4219k & 50\\
\hline
\end{tabular}

 \caption{Na\"{i}ve Bayes results. We compare our results (columns 6 , 7, 8) with~\cite{shafindss} (columns 4 and 5)}
 \label{tab:nb} 
\end{table*}

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c|c}
Dataset  & $N$ & Prev. time (s) & Prev. Comm (kb) & LAN time (s) & WAN time (s) & Comm. (kb)  & \#And & \#Mul & \#Gates & LOC\\
\hline
Nursery & 4 & 0.3 & 102 & 0.1 & 0.3 & 32 & 504 & 3 & 3324 & 20\\
\hline
ECG &  6 & 0.4 & 102 & 0.1 & 0.4 & 49 & 756 & 5 & 5002 & 20\\
\hline
\end{tabular}

 \caption{Decision tree benchmarks. We compare our results (columns 5 , 6, 7) with~\cite{wu} (columns 3 and 4)}
 \label{tab:dt} 
\end{table*}

@@

In Table~\ref{tab:nn}, columns 2 and 3 show the time taken by \minion.
The column ``Model size'' is the number of parameters in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient
preprocessing phase and has SIMD 
(single instruction multiple data) capabilities that allow it to perform
matrix operations efficiently. In contrast, \tool focuses on generic
2PC, and such optimizations are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length 
\setlength\tabcolsep{6.5pt}
\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c|c}
DNN  & Prev. time (s) & Prev. Comm (Mb) & LAN (s) & WAN (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & Model Size & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &  2k   & 119k & 366k   & 119k & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 70    & 2k    & 108k & 316k & 86k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 1640k & 667k & 9480k & 35k & 154\\
\hline
\end{tabular}

 \caption{DNN benchmarks. We compare our results (columns 4 , 5, 6) with~\cite{minionn} (columns 2 and 3)}
 \label{tab:nn} 
\end{table*}

@@

% benchmark | size | gates | and | mul | depth  | length | comm | timeL | timeW
\setlength\tabcolsep{2.5pt}
\begin{table}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c | c}
Classifier       & \thead{LAN  \\ (s)} & \thead{WAN \\(s)} & \thead{Comm. \\(Mb)}  & \#And & \#Mul & \#Gates & \thead{Model \\size} & LOC\\
\hline
Regression &  0.1         & 0.7         & 5            & 2k    & 8k    &  35k    & 8k   & 38\\
\hline
CNN        &  30.5        & 60.3        & 2955         & 6082k & 4163k &  42104k & 3226k& 172\\
\hline
\end{tabular}

@@

\setlength\tabcolsep{3.5pt}
\begin{table}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c | c}
Dataset       & \thead{LAN \\(s)} & \thead{WAN \\(s)} & \thead{Comm. \\ (Mb)}  & \#And & \#Mul & \#Gates & depth & LOC\\
\hline
Chars4k    &  0.1         & 0.7         & 2            & 18k    & 3k    &  85k     & 1   & 89\\
\hline
USPS       &  0.2         & 0.9         & 4            & 62k    & 2k    &  285k    & 2   & 156\\
\hline
WARD       &  0.3         & 1.1         & 9            & 106k    & 8k    &  506k    & 3   & 283\\
\hline
\end{tabular}

@@

Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth (the heaviest) stage. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
For this DNN, the specialized \minion protocol takes 544 seconds and
communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to arbitrary sized
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion could run
out of memory but an appropriately partitioned \tool implementation would still
succeed. 
\begin{table}
\begin{tabular}{c|c|c|c |c|c|c}
           &  LAN (s) & WAN (s) & \thead{Comm. \\ (Mb)}  & \#And & \#Mul & \#Gates \\
\hline
Total      &  265.6       & 647.5        & 40683       & 21m    & 61m    &  337m  \\
\hline
Stage 6    &  55.2        & 122.6        & 6744        & 12m    & 10m   &  98m  \\
\hline
\end{tabular}

>>>>

\subsubsection*{Linear classifier}The results for linear
classification are in Table~\ref{tab:lc}. The
input and the model are both vectors of length $d$. The columns
``Prev. time'' and ``Prev. comm'' show the time and the total
network communication reported by Bost et al.~\cite{shafindss} for a
network setting with 40ms
round trip time, which is same as our WAN setting. The total execution
time
of \tool generated code in the LAN and the WAN setting is reported
next, followed by the total communication.
We observe that the \tool code performance matches the hand-crafted protocol of Bost
et al., and the programmer effort in \tool is just 20
lines (last column in the table) of high-level code in the \tool
source language. %\aseem{They write circuits,
 % right?} \nc{Actually, they have a specific protocols for dot product and comparison and also say that their developer effort is minimal as they have to write two function calls to these protocols :).} 
% Our execution time is dominated by the multiplications and
%boolean-ands.
%The number of boolean-and gates (\#And) remains constant for both the
%benchmarks as they reflect the number of gates required for a
%single  comparison, while the number of
%multiplication gates (\#Mul) is the same as the model size $d$.
%% The
%% last column shows the lines of code of \tool program, which is also
%% independent of the model size.

%\setlength\tabcolsep{7pt}
%\begin{table*}
%\begin{tabular}{c|c|c|c|c |c|c|c|c|c|c}
%Dataset & $d$  & Prev. time (s) & Prev. Comm (kb) & LAN (s) & WAN (s) & Comm. (kb)  & \#And & \#Mul & \#Gates & LOC\\
%\hline
%Breast cancer & 30 & 0.3 & 36 & 0.1 & 0.3 & 25 & 95 & 30 & 727 & 20\\
%\hline
%Credit & 47 & 0.3 & 41 & 0.1 & 0.3 & 36 & 95 & 47 & 795 & 20\\
%\hline
%\end{tabular}

\setlength\tabcolsep{2.5pt}
\begin{table}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Dataset & $d$  & \thead{Prev. \\ time\\ (s)} & \thead{Prev. \\ Comm\\ (kb)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm. \\(kb)}  &  \#Gates & LOC\\
\hline
Breast cancer & 30 & 0.3 & 36 & 0.1 & 0.3 & 25  & 727 & 20\\
\hline
Credit & 47 & 0.3 & 41 & 0.1 & 0.3 & 36  & 795 & 20\\
\hline
\end{tabular}
 \caption{Linear classification results. We compare our results (columns 5, 6, 7) with~\cite{shafindss} (columns 3 and 4)}
 \label{tab:lc} 
\end{table}

@@

\setlength\tabcolsep{2.5pt}
\begin{table}
\begin{tabular}{|c|c|c|c|c|c |c|c|c|c|}
\hline
Dataset & $d$ & $F$ & \thead{Prev. \\ time\\ (s)} & \thead{Prev. \\ Comm\\ (kb)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm. \\(kb)} & \#Gates  & LOC\\
\hline
Nursery & 5 & 9 & 1.5 & 0.2 & 0.1 & 0.4 & 0.6  & 73k & 50\\
\hline
Audiology & 24 & 70 & 3.9 & 2.0 & 1.5 & 2.9 & 37  & 4219k & 50\\
\hline
\end{tabular}
\caption{Na\"{i}ve Bayes results. We compare our results (columns 6 , 7, 8) with~\cite{shafindss} (columns 4 and 5)}
 \label{tab:nb} 
\end{table}

\subsubsection*{Decision trees}
Our decision tree numbers in Table~\ref{tab:dt} further validate
this claim. We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
describe specialized protocols for trees and forests (that perform
better than~\cite{shafindss}).
Similar to Bost et al.~\cite{shafindss}, they also remarks that these
computations are infeasible with Yao-based 2PC.
Again, we observe that
the performance of \tool generated generic 2PC
code is competitive with specialized protocols.

%\begin{table*}
%\begin{tabular}{|c|c|c|c |c|c|c|c|c|c|c|}
%\hline
%Dataset  & $N$ & \thead{Prev. \\ time\\ (s)} & \thead{Prev. \\ Comm\\ (kb)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm. \\(kb)}& \#And & \#Mul &\#Gates & LOC\\
%\hline
%Nursery & 4 & 0.3 & 102 & 0.1 & 0.3 & 32 & 504 & 3 & 3324 & 20\\
%\hline
%ECG &  6 & 0.4 & 102 & 0.1 & 0.4 & 49 & 756 & 5 & 5002 & 20\\
%\hline
%\end{tabular}
% \caption{Decision tree benchmarks. We compare our results (columns 5 , 6, 7) with~\cite{wu} (columns 3 and 4)}
% \label{tab:dt} 
%\end{table*}

\begin{table}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Dataset  & $N$ & \thead{Prev. \\ time\\ (s)} & \thead{Prev. \\ Comm\\ (kb)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm. \\(kb)}& \#Gates & LOC\\
\hline
Nursery & 4 & 0.3 & 102 & 0.1 & 0.3 & 32 & 3324 & 20\\
\hline
ECG &  6 & 0.4 & 102 & 0.1 & 0.4 & 49  & 5002 & 20\\
\hline
\end{tabular}
\caption{Decision tree benchmarks. We compare our results (columns 5 , 6, 7) with~\cite{wu} (columns 3 and 4)}
 \label{tab:dt} 
\end{table}

@@

In Table~\ref{tab:nn}, columns 2 and 3 show the time taken by \minion.
The column ``Model size'' is the number of parameters in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient
preprocessing phase and has SIMD 
(single instruction multiple data) capabilities that allow it to perform
matrix operations efficiently. In contrast, \tool focuses on generic
2PC, and such optimizations are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length

%\setlength\tabcolsep{6.5pt}
%\begin{table*}
%\begin{tabular}{c|c|c|c |c|c|c|c|c|c|c}
%DNN  & Prev. time (s) & Prev. Comm (Mb) & LAN (s) & WAN (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & Model Size & LOC\\
%\hline
%SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &  2k   & 119k & 366k   & 119k & 78\\
%\hline
%Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 70    & 2k    & 108k & 316k & 86k & 88\\
%\hline
%CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 1640k & 667k & 9480k & 35k & 154\\
%\hline
%\end{tabular}
%
% \caption{DNN benchmarks. We compare our results (columns 4 , 5, 6) with~\cite{minionn} (columns 2 and 3)}
% \label{tab:nn} 
%\end{table*}

\setlength\tabcolsep{2.5pt}
\begin{table}
\begin{tabular}{|c|c|c|c |c|c|c|c|c|}
\hline
DNN  & \thead{Prev. \\ time\\ (s)} & \thead{Prev. \\ Comm\\ (kb)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm. \\(kb)} & \#Gates & \thead{Model\\ Size} & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &   366k   & 119k & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 70    &  316k & 86k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 9480k & 35k & 154\\
\hline
\end{tabular}

 \caption{DNN benchmarks. We compare our results (columns 4 , 5, 6) with~\cite{minionn} (columns 2 and 3)}
 \label{tab:nn} 
\end{table}

@@

% benchmark | size | gates | and | mul | depth  | length | comm | timeL | timeW
\setlength\tabcolsep{2.5pt}
\begin{table}
\begin{tabular}{|c|c|c|c |c|c|c|c|c|c | c}
\hline
Classifier       & \thead{LAN  \\ (s)} & \thead{WAN \\(s)} & \thead{Comm. \\(Mb)}  & \#And & \#Mul & \#Gates & \thead{Model \\size} & LOC\\
\hline
Regression &  0.1         & 0.7         & 5            & 2k    & 8k    &  35k    & 8k   & 38\\
\hline
CNN        &  30.5        & 60.3        & 2955         & 6082k & 4163k &  42104k & 3226k& 172\\
\hline
\end{tabular}

@@

\setlength\tabcolsep{3.5pt}
\begin{table}
\begin{tabular}{|c|c|c|c |c|c|c|c|c|c | c|}
\hline
Dataset       & \thead{LAN \\(s)} & \thead{WAN \\(s)} & \thead{Comm. \\ (Mb)}  & \#And & \#Mul & \#Gates & depth & LOC\\
\hline
Chars4k    &  0.1         & 0.7         & 2            & 18k    & 3k    &  85k     & 1   & 89\\
\hline
USPS       &  0.2         & 0.9         & 4            & 62k    & 2k    &  285k    & 2   & 156\\
\hline
WARD       &  0.3         & 1.1         & 9            & 106k    & 8k    &  506k    & 3   & 283\\
\hline
\end{tabular}

@@

Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth (the heaviest) stage. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
For this DNN, the specialized \minion protocol takes 544 seconds and
communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to arbitrary sized
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion could run
out of memory but an appropriately partitioned \tool implementation would still
succeed. 
\begin{table}
\begin{tabular}{|c|c|c|c |c|c|c|}
\hline
           &  LAN (s) & WAN (s) & \thead{Comm. \\ (Mb)}  & \#And & \#Mul & \#Gates \\
\hline
Total      &  265.6       & 647.5        & 40683       & 21m    & 61m    &  337m  \\
\hline
Stage 6    &  55.2        & 122.6        & 6744        & 12m    & 10m   &  98m  \\
\hline
\end{tabular}
